\textit{MSF: Modulated Sub-graph Finder}

### 2018-02-26 MSF_Paper_FA.tex
remove paths to figures

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/Tgfb1} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/TGFBstep1}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/TGFBstep2} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/TGFBstep3}
		\caption{}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing the steps to identify the modulated sub-graphs. (a) showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) the genes circled red show the two initial modulated sub-graphs, sub-graph1 found one with M,K,C and the second modulated sub-graph2 S,V,T, (c) shows the modulated sub-graph1 being extended to M,K,C,A,D, (d) shows both the modulated sub-graphs merged with the addition of 3 genes Z,W,P.}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=1.6\linewidth]{Git/MSF_Paper/Merged6hNetwork}
	\caption{Modulated Sub-graph from 6hpi, showing KEGG predefined pathways colored.}
	\label{fig:merged6hnetwork}
\end{figure*}

\begin{figure*}[p]
	\includegraphics[width=16cm]{Git/MSF_Paper/DEGvsMSF2}
	\caption{Robustness analysis for three time-points of infection}
	\label{fig:degvsmsf2}
\end{figure*}

>>>>

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Tgfb1.png} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep2.png} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep3.png}
		\caption{}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing the steps to identify the modulated sub-graphs. (a) showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) the genes circled red show the two initial modulated sub-graphs, sub-graph1 found one with M,K,C and the second modulated sub-graph2 S,V,T, (c) shows the modulated sub-graph1 being extended to M,K,C,A,D, (d) shows both the modulated sub-graphs merged with the addition of 3 genes Z,W,P.}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=1.6\linewidth]{Merged6hNetwork.png}
	\caption{Modulated Sub-graph from 6hpi, showing KEGG predefined pathways colored.}
	\label{fig:merged6hnetwork}
\end{figure*}

\begin{figure*}[p]
	\includegraphics[width=16cm]{DEGvsMSF2.png}
	\caption{Robustness analysis for three time-points of infection}
	\label{fig:degvsmsf2}
\end{figure*}
